### 2014-11-10 Paper1/paper1.tex
updated table 1

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}
\usepackage[section]{placeins}

@@

\begin{table}[!ht]
\caption{
\bf{Arm Parameter Values and Sensitivities}}
\begin{tabular}{|c|c|c c|c c|c c|c|}
\hline
Parameter Name &
Units &
Nominal &
Source &
SD &
Source &
$S$ &
$S_T$ \\ \hline
Upper Arm Length ($L_1$) &
m &
0.353 &
\cite{dempster1955space} &
0.017 &
\cite{dempster1955space} &
0 &
0.10 \\
Forearm Length ($L_2$) &
m &
0.363 &
\cite{dempster1955space} &
0.011 &
\cite{dempster1955space} &
0 &
0.03 \\
Upper Arm Center of Mass Ratio ($\frac{L_{m1}}{L_1}$) &
1 &
0.436 &
\cite{winter2009biomechanics} &
0.0695 &
15\% &
0 &
0.02 \\
Forearm Center of Mass Ratio ($\frac{L_{m2}}{L_2}$) &
1 &
0.682 &
\cite{winter2009biomechanics} &
0.0431 &
15\% &
0 &
0.02 \\
Gross Body Mass ($m_g$) &
kg &
88.4 &
\cite{fryar2012anthropometric} &
3.1 &
\cite{stunkard1981accuracy} &
0 &
0.02 \\
Upper Arm Mass Ratio ($\frac{m_1}{m_g}$) &
1 &
0.028 &
\cite{winter2009biomechanics} &
0.0029 &
\cite{dempster1955space} &
0 &
0.01 \\
Forearm Mass Ratio ($\frac{m_2}{m_g}$) &
1 &
0.022 &
\cite{winter2009biomechanics} &
0.0025 &
\cite{dempster1955space} &
0 &
0.06 \\
Upper Arm Radius of Gyration Ratio &
1 &
0.322 &
\cite{winter2009biomechanics} &
0.0161 &
15\% &
0 &
0.01 \\
Forearm Radius of Gyration Ratio &
1 &
0.468 &
\cite{winter2009biomechanics} &
0.0234 &
15\% &
0 &
0.01 \\
Shoulder Parallel Coordinate &
m &
-0.057 &
RM &
0.02 &
RM &
0.02 &
0.18 \\
Shoulder Perpendicular Coordinate &
m &
0.88 &
RM &
0.02 &
RM &
0 &
0.08 \\
Force Sensor Miscalibration $x\text{-axis}$ &
N &
0 &
RM &
0.231 &
RM &
0 &
0.08 \\
Force Sensor Miscalibration $y\text{-axis}$ &
N &
0 &
RM &
0.1067 &
RM &
0.03 &
0.08 \\
Force Sensor Gaussian Noise SD $x\text{-axis}$ &
N &
0 &
RM &
0.1653 &
RM &
0 &
0.01 \\
Force Sensor Gaussian Noise SD $y\text{-axis}$ &
N &
0 &
RM &
0.2869 &
RM &
0 &
0.01 \\
Torque-Invariant Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
15\% &
0.06 &
0.31 \\
Torque-Varying Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
15\% &
0 &
0.15 \\
Damping-to-Stiffness Ratio ($k_d$) &
$\text{sec}^{-1}$ &
0.0833 &
\cite{burdet2006stability} &
0.0125 &
15\% &
0 &
0.08 \\
Reflex Impedance Scale Factor &
1 &
0.02 &
\cite{burdet2006stability} &
0.003 &
15\% &
0 &
0.04 \\
Reflex Damping to Stiffness Ratio ($g_d$) &
$\text{sec}^{-1}$ &
2 &
\cite{burdet2006stability} &
0.3 &
15\% &
0 &
0.04 \\ \hline
\end{tabular}
\begin{flushleft}Synthetic model parameters and their associated mean (nominal) values and standard deviations (SD) used to determine the sensitivity indices of Saltelli et al. \cite{saltelli2010variance}. Also shown are the resulting sensitivity indices. Sensitivity indices less than one-thousandth were reported as zero. Total variance was $1.3 \mu m^2$, showing very small average deviations when using this approach. First-order sensitivity, $S$, can be interpreted as fraction of variance removable by perfectly correcting a factor. Total sensitivity, $S_T$, can be interpreted as the fraction left after correcting all other factors. Most parameter values come from the literature, but instrument-specific parameters were determined empirically through repeated measurements (RM). Where parameter values were unavailable, 15\% of the mean was used as a conservative estimate
\end{flushleft}
\label{tab:parameters}
\end{table}

>>>>

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% PLoS doesn't support/use the next package, but we get issues if we don't use this to generate the PDF. Comment this line out when submitting.
\usepackage[section]{placeins}

@@

\begin{table}[!ht]
\caption{
\bf{Arm Parameter Values and Sensitivities}}
\begin{tabular}{|c|c|c c|c c|c c|c|}
\hline
Parameter Name &
Units &
Nominal &
Source &
SD &
Source &
$S$ &
$S_T$ \\ \hline
Upper Arm Length ($L_1$) &
m &
0.353 &
\cite{dempster1955space} &
0.017 &
\cite{dempster1955space} &
0.03 &
0.17 \\
Forearm Length ($L_2$) &
m &
0.363 &
\cite{dempster1955space} &
0.011 &
\cite{dempster1955space} &
0 &
0.03 \\
Upper Arm Center of Mass Ratio ($\frac{L_{m1}}{L_1}$) &
1 &
0.436 &
\cite{winter2009biomechanics} &
0.0695 &
15\% &
0 &
0.02 \\
Forearm Center of Mass Ratio ($\frac{L_{m2}}{L_2}$) &
1 &
0.682 &
\cite{winter2009biomechanics} &
0.0431 &
15\% &
0.01 &
0.07 \\
Gross Body Mass ($m_g$) &
kg &
88.4 &
\cite{fryar2012anthropometric} &
3.1 &
\cite{stunkard1981accuracy} &
0 &
0.02 \\
Upper Arm Mass Ratio ($\frac{m_1}{m_g}$) &
1 &
0.028 &
\cite{winter2009biomechanics} &
0.0029 &
\cite{dempster1955space} &
0 &
0.01 \\
Forearm Mass Ratio ($\frac{m_2}{m_g}$) &
1 &
0.022 &
\cite{winter2009biomechanics} &
0.0025 &
\cite{dempster1955space} &
0 &
0.06 \\
Upper Arm Radius of Gyration Ratio &
1 &
0.322 &
\cite{winter2009biomechanics} &
0.0161 &
15\% &
0.01 &
0.06 \\
Forearm Radius of Gyration Ratio &
1 &
0.468 &
\cite{winter2009biomechanics} &
0.0234 &
15\% &
0 &
0.04 \\
Shoulder Parallel Coordinate &
m &
-0.057 &
RM &
0.02 &
RM &
0.01 &
0.14 \\
Shoulder Perpendicular Coordinate &
m &
0.88 &
RM &
0.02 &
RM &
0.02 &
0.06 \\
Force Sensor Miscalibration $x\text{-axis}$ &
N &
0 &
RM &
0.231 &
RM &
0.01 &
0.05 \\
Force Sensor Miscalibration $y\text{-axis}$ &
N &
0 &
RM &
0.1067 &
RM &
0.03 &
0.08 \\
Force Sensor Gaussian Noise SD $x\text{-axis}$ &
N &
0 &
RM &
0.1653 &
RM &
0 &
0.01 \\
Force Sensor Gaussian Noise SD $y\text{-axis}$ &
N &
0 &
RM &
0.2869 &
RM &
0 &
0.01 \\
Torque-Invariant Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
15\% &
0.05 &
0.19 \\
Torque-Varying Impedance Misestimation Ratio &
1 &
1 &
\cite{burdet2006stability} &
0.15 &
15\% &
0.05 &
0.19 \\
Damping-to-Stiffness Ratio ($k_d$) &
$\text{sec}^{-1}$ &
0.0833 &
\cite{burdet2006stability} &
0.0125 &
15\% &
0.01 &
0.08 \\
Reflex Impedance Scale Factor &
1 &
0.02 &
\cite{burdet2006stability} &
0.003 &
15\% &
0.01 &
0.04 \\
Reflex Damping to Stiffness Ratio ($g_d$) &
$\text{sec}^{-1}$ &
2 &
\cite{burdet2006stability} &
0.3 &
15\% &
0 &
0.04 \\ \hline
\end{tabular}
\begin{flushleft}Synthetic model parameters and their associated mean (nominal) values and standard deviations (SD) used to determine the sensitivity indices of Saltelli et al. \cite{saltelli2010variance}. Also shown are the resulting sensitivity indices. Sensitivity indices less than one-thousandth were reported as zero. Total variance was $1.56 mm^2$, showing very small average deviations when using this approach. First-order sensitivity, $S$, can be interpreted as fraction of variance removable by perfectly correcting a factor. Total sensitivity, $S_T$, can be interpreted as the fraction left after correcting all other factors. Most parameter values come from the literature, but instrument-specific parameters were determined empirically through repeated measurements (RM). Where parameter values were unavailable, 15\% of the mean was used as a conservative estimate.
\end{flushleft}
\label{tab:parameters}
\end{table}
